### 2014-11-04 Projects/DelCo_2012/Report/DelCo_2012.tex

\begin{sidewaystable}[!ht]
	\centering
	\caption{Test Descriptions}
	\begin{tabular}{lllllllll}
		\hline\noalign{\smallskip}
		Test		& Agent		& Stream		& Flow Rate		& Comments		& Nozzle 1 Activation		& Nozzle 1 Shut Off		& Nozzle 2 Activation		& Nozzle 2 Shut Off \\
		\noalign{\smallskip}\hline\noalign{\smallskip}
		1 (FSE1)    &  CAF      &  30 deg Fog  	&  120 gpm/60 cfm    \\
		2 (FSW2)   	& Water     &  30 deg Fog  	&  120 gpm    \\
		3 (FSW3) 	&  CAF      &  7/8" Smooth Bore  &  120 gpm/60 cfm    \\
		4 (FSE4)    &  Water    &  7/8" Smooth Bore  &  120 gpm    \\
		5 (FSE5)    &  Water    &  30 deg Fog  	&  120 gpm    \\
		6 (FSW6)    &  CAF      &  30 deg Fog  	&  120 gpm/60 cfm    \\
		7 (FSW7)    &  Water    &  30 deg Fog  	&  120 gpm    \\
		8 (FSE8)    &  CAF      &  30 deg Fog  	&  120 gpm/60 cfm    \\
		9 (Attic 1) &  Water    &  Straight Stream  &  120 gpm    \\
		10 (Attic 2)&  CAF      &  Straight Stream  &  120 gpm/60 cfm    \\
		11 (FSE1)   &  Water    &  30 deg Fog  	&  120 gpm    \\
		12 (FSW1)   &  CAF      &  30 deg Fog  	&  120 gpm/60 cfm    \\
		13 (FSE2)   &  Water    &  30 deg Fog  	&  120 gpm    \\
		14 (FSW2)   &  CAF      &  30 deg Fog  	&  120 gpm/60 cfm    \\
		\noalign{\smallskip}\hline
	\end{tabular}
	\label{tab:Fuel_Masses}
\end{sidewaystable}

>>>>

\begin{sidewaystable}[!ht]
	\centering
	\caption{Test Descriptions}
	\begin{tabular}{lllll}
		\hline\noalign{\smallskip}
		Test		& Agent		& Stream		& Flow Rate		& Comments \\
		\noalign{\smallskip}\hline\noalign{\smallskip}
		1 (FSE1)    &  CAF      &  30 deg Fog  	&  120 gpm/60 cfm    \\
		2 (FSW2)   	& Water     &  30 deg Fog  	&  120 gpm    \\
		3 (FSW3) 	&  CAF      &  7/8" Smooth Bore  &  120 gpm/60 cfm    \\
		4 (FSE4)    &  Water    &  7/8" Smooth Bore  &  120 gpm    \\
		5 (FSE5)    &  Water    &  30 deg Fog  	&  120 gpm    \\
		6 (FSW6)    &  CAF      &  30 deg Fog  	&  120 gpm/60 cfm    \\
		7 (FSW7)    &  Water    &  30 deg Fog  	&  120 gpm    \\
		8 (FSE8)    &  CAF      &  30 deg Fog  	&  120 gpm/60 cfm    \\
		9 (Attic 1) &  Water    &  Straight Stream  &  120 gpm    \\
		10 (Attic 2)&  CAF      &  Straight Stream  &  120 gpm/60 cfm    \\
		11 (FSE1)   &  Water    &  30 deg Fog  	&  120 gpm    \\
		12 (FSW1)   &  CAF      &  30 deg Fog  	&  120 gpm/60 cfm    \\
		13 (FSE2)   &  Water    &  30 deg Fog  	&  120 gpm    \\
		14 (FSW2)   &  CAF      &  30 deg Fog  	&  120 gpm/60 cfm    \\
		\noalign{\smallskip}\hline
	\end{tabular}
	\label{tab:Test_Descriptions}
\end{sidewaystable}

\begin{sidewaystable}[!ht]
	\centering
	\caption{Nozzle Activation Times}
	\begin{tabular}{lllllllll}
		\hline\noalign{\smallskip}
		Test		& Agent		& Stream				& Nozzle 1 Activation		& Nozzle 1 Shut Off		& Nozzle 2 Activation		& Nozzle 2 Shut Off \\
		\noalign{\smallskip}\hline\noalign{\smallskip}
		1 (FSE1)    &  CAF      &  30 deg Fog  	    \\
		2 (FSW2)   	& Water     &  30 deg Fog  	    \\
		3 (FSW3) 	&  CAF      &  7/8" Smooth Bore      \\
		4 (FSE4)    &  Water    &  7/8" Smooth Bore     \\
		5 (FSE5)    &  Water    &  30 deg Fog  	    \\
		6 (FSW6)    &  CAF      &  30 deg Fog      \\
		7 (FSW7)    &  Water    &  30 deg Fog      \\
		8 (FSE8)    &  CAF      &  30 deg Fog      \\
		9 (Attic 1) &  Water    &  Straight Stream      \\
		10 (Attic 2)&  CAF      &  Straight Stream      \\
		11 (FSE1)   &  Water    &  30 deg Fog  	    \\
		12 (FSW1)   &  CAF      &  30 deg Fog  	    \\
		13 (FSE2)   &  Water    &  30 deg Fog  	   \\
		14 (FSW2)   &  CAF      &  30 deg Fog  	   \\
		\noalign{\smallskip}\hline
	\end{tabular}
	\label{tab:Nozzle_Activation_Times}
\end{sidewaystable}
